---
title: "Assignement 1"
author: "Nikita Sotnikov"
date: "16 01 2021"
output:
  html_document: default
  pdf_document: default
---
#Question 1
```{r}
House=read.csv("kc house sales.csv")
attach(House)
```
#Question 2
```{r}
summary(House)
```
#Question 3
```{r}
date=as.Date(date,format="%Y%m%d")
```
#Question 4
```{r}
view=as.factor(view)
waterfront=as.factor(waterfront)
zipcode=as.factor(zipcode)
```
#Question 5
```{r}
summary(House)
```
#No, the variables in this summary are treated as numerical and not categorical

#Question 6
```{r}
summary(data.frame(date,view,waterfront,zipcode))
```
#Yes, Because Question 6 uses command data.frame which categorized the value.

#Question 7
```{r}
House=data.frame(House[,-c(1, 8:9, 16)], date, view, waterfront, zipcode)
summary(House)
```
#Question 8
```{r}
unique(zipcode) 
```
# 70 levels

#Question 9
```{r}
pairs(House[,1:3])
```
#Question 10
```{r}
table(bedrooms)
```
#33 bedrooms is unusual observation

#Question 11
```{r}
House[bedrooms>30,]
```
#Question 12
```{r}
House[15871, 2]=3
detach(House)
attach(House)
```
#Question 13
```{r}
pairs(House[,1:3])
```
# Price depends from number of bedrooms and bathrooms

#Question 14
```{r}
plot(waterfront,price)
plot(view,price)
```
#Question 15
```{r}
hist(price)
hist(price, breaks=30, col=2)
hist(sqft_living, col="green")
hist(sqft_lot)
hist(sqft_lot[sqft_lot<30000], col="gray")
```
#Question 16
```{r}
par(mfcol=c(2,2))
plot(waterfront,price)
plot(view,price)
hist(price)
hist(price, breaks=30, col=2)
hist(sqft_living, col="green")
hist(sqft_lot)
hist(sqft_lot[sqft_lot<30000], col="grey")
```
#Question 17
```{r}
ranges=sapply(House[,1:16],range)
```
#Question 18
```{r}
ranges
ranges[2,]
```
#Question 19
```{r}
mansion=rep("No", nrow(House))
mansion[sqft_living15>5000]="Yes"
mansion=as.factor(mansion)
```
#Question 20
```{r}
summary(mansion)
```
#22 mansions was sold during the period

#Question 21
```{r}
plot(price,mansion)
```
#Question 22
```{r}
House.wf=subset(House,waterfront==1)
mean(House.wf[,1])
summary(House.wf)
```
#Question 23
```{r}
House.old=subset(House,yr_built<=1920)
dim(House.old)
```